### 2023-09-02 sections/2-methods.tex
minor explanation

Once $|H| > 0$, we continue to perform $\rho$-NN search, but instead of 
increasing the radius by a factor of 2 on each iteration, we increase it by a factor determined 
by the local fractal dimension in the region of the dataset around the query ball. 
In particular, 
we increase the radius by a factor of 
\begin{equation} \argmin \left(2, \left({\frac{k}{|H|}}\right)^{\frac{1}{\mu}}\right) \label{2} \end{equation}
where $\mu$ is the harmonic mean of the local fractal dimensions (abbreviated lfd in algorithm below) of 
each cluster which contains one of the nearest neighbors found thus far. We use the harmonic mean to 
ensure that $\mu$ is not dominated by outlier clusters with very high fractal dimension. 
Intuitively, the factor by which we increase the radius should be \emph{inversely} related to the number of points found so far. 
Additionally, when the local fractal dimension at the radius scale from the previous iteration is low, this suggests that the data 
are relatively concentrated in that region; thus, the factor of radius increase should be \emph{directly} related to the 
local fractal dimension. Once $|H| >= k$, we return the $k$ closest points.

>>>>

Once $|H| > 0$, we continue to perform $\rho$-NN search, but instead of 
increasing the radius by a factor of 2 on each iteration, we increase it by a factor determined 
by the local fractal dimension in the region of the dataset around the query ball. 
In particular, 
we increase the radius by a factor of 
\begin{equation} \argmin \left(2, \left({\frac{k}{|H|}}\right)^{\frac{1}{\mu}}\right) \label{2} \end{equation}
where $\mu$ is the harmonic mean of the local fractal dimensions (abbreviated lfd in algorithm below) of 
each cluster which contains one of the nearest neighbors found thus far. We use the harmonic mean to 
ensure that $\mu$ is not dominated by outlier clusters with very high fractal dimension. 
Intuitively, the factor by which we increase the radius should be \emph{inversely} related to the number of points found so far. 
Additionally, when the local fractal dimension at the radius scale from the previous iteration is low, this suggests that the data 
are relatively concentrated in that region; in other words, a small increase in the radius would likely encounter unoccupied space around the manifold, so a larger radius increase is needed. Thus, in this case, the factor of radius increase should be \emph{directly} related to the 
local fractal dimension. Once $|H| >= k$, we return the $k$ closest points.
